---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%",
  dpi = 300
)
options(tibble.max_extra_cols = 20)
ggplot2::theme_set(ggplot2::theme_minimal())
```

# lemur

CMHC Housing Supply Challenge Proof of Concept

## Installation

You can install lemur from GitHub:

``` r
# install.packages("devtools")
devtools::install_github("purposeanalytics/lemur")
```

## Usage

### App

The primary product of lemur is a Shiny app which will show low-end of market rental housing in Toronto, along with other data sets. To load the app, run:

```r
lemur::run_app()
```

### Functions

lemur also contains a few utility functions.

For example, you can geocode addresses using the Bing geocoder:

```{r}
library(lemur)
geocode_address("220 Yonge St Toronto ON")
```

This looks up any address in Canada, so it's helpful to supply the city or postal code for the most accurate results - for example, 220 Yonge St without "Toronto ON" gives us somewhere on an island in Lake Huron:

```{r}
geocode_address("220 Yonge St")
```

An API token is required, and the function looks for it in the `BING_TOKEN` environment variable, buit this can be changed or supplied directly via the `token` argument.

### Data sets

lemur contains a number of spatial data sets (used in the app), which can also be used in other code or packages.

#### toronto

toronto is a data set that includes the boundary of Toronto:

```{r}
library(sf)
library(ggplot2)
toronto

p <- ggplot() + 
  geom_sf(data = toronto)

p
```

#### neighbourhoods

neighbourhoods contains the 140 social planning neighbourhoods in Toronto and their boundaries. Once the [new 158 neighbourhoods](https://www.toronto.ca/city-government/data-research-maps/neighbourhoods-communities/neighbourhood-profiles/) are released by the City of Toronto, this data set will be updated.

```{r}
neighbourhoods

p <- p +
  geom_sf(data = neighbourhoods)

p
```
 
#### apartment_building_registry

apartment_building_registry is a geocoded version of the City of Toronto's [Apartment Building Registration Dataset](https://open.toronto.ca/dataset/apartment-building-registration/), with cleaned addresses and latitude and longitude:

```{r}
apartment_building_registry

p + 
  geom_point(data = apartment_building_registry, aes(x = bing_longitude, y = bing_latitude))
```
