---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lemur

CMHC Housing Supply Challenge Proof of Concept

## Installation

You can install lemur from GitHub:

``` r
# install.packages("devtools")
devtools::install_github("purposeanalytics/lemur")
```

## Usage

To load the app, run:

```r
lemur::run_app()
```

lemur also contains a utility function for geocoding addresses using the Bing geocoder:

```{r}
library(lemur)
geocode_address("220 Yonge St Toronto ON")
```

This looks up any address in Canada, so it's helpful to supply the city or postal code for the most accurate results - for example, 220 Yonge St without "Toronto ON" gives us somewhere on an island in Lake Huron:

```{r}
geocode_address("220 Yonge St")
```

An API token is required, and the function looks for it in the `BING_TOKEN` environment variable, buit this can be changed or supplied directly via the `token` argument.
